Progress

### 2018-07-16 two_dim_majoranas_report/progress.tex
switch l_m <-> l_r
put sentences on seperate lines

	\begin{align}
		H &= H_0(\tau_z \otimes \sigma_0) + 
		H_\text{Z} (\tau_0 \otimes \sigma_z) +
		(\tau_z \otimes H_\text{SO}) +
	 H_\text{SC}(\tau_y \otimes \sigma_0) \\
		H_0 &= \frac{\hbar^2}{2\meff}\left(\kx^2 + \ky^2\right) - \mu \\
		H_\text{Z} &= g \mu_B B  \left(\Theta(-x) - \Theta(L_m-x)\right)  \\
		H_\text{SO} &= \alpha \left( \ky \sigma_x - \kx \sigma_y \right)\\
		H_\text{SC} &= \Delta \exp \left(i \theta \Theta(x-L_m) \right)
	\end{align}
	Where: 
	\begin{equation}
	\Theta(x) = 
	\begin{cases}
	1,& x>0\\
	0,& \text{otherwise}
	\end{cases}
	\end{equation}
	\subsection{Assumptions and limitations of model}
%		[TODO: LIST ASSUMPTIONS AND LIMITATIONS: SPIN ORBIT DRESSELHAUS, SC MODEL, ETC.]
	\subsection{System parameters}
	\begin{table}
		\begin{tabular}{|c|c|c|c|}
			\hline 
			Variable & Description & Typical value & Default value \\ 
			\hline 
			$g_\text{factor}$ & Magnetic g-factor of material & ~10 & 10 \\ 
			\hline 
			$\mu$ & Chemical potential &  10 - 30 meV & 1 meV\\ 
			\hline 
			$\alpha$ & Spin orbit coupling strength &  30 meV nm & 30 meV nm \\ 
			\hline 
			$\Delta$ & Superconducting gap & 0.2 - 0.3 meV & 0.18 meV\\ 
			\hline 
			$B$ & In-plane magnetic field strength along stripe direction(y) & 0 - 1 T & 0.2 T \\ 
			\hline 
			$\phi$ & Relative phase between superconductors &  0 - 2$\pi$ & $\pi$\\ 
			\hline 
			$\text{L}_\text{l}$ & Width of left superconductor & $\infty$ & 500 nm \\
			\hline 
			$\text{L}_\text{m}$ & Width of right superconductor & $\infty$ & 500 nm \\
			\hline
			$\text{L}_\text{r}$ & Width of middle "normal" strip & 100 - 1000 nm & 250 nm \\
			\hline
			$\text{L}_\text{y}$ & Length of system & \textgreater1000 nm & 4000 nm\\
			\hline
			$T$ & Temperature of system & 0.25 - 1.2K & 0 K\\
			\hline
		\end{tabular} 
	\caption{Description of system parameters, along with typical valuses, as well as a default value which is the used value when no other value has been specified.}
	\label{tbl:system_pars}
	\end{table}
	Describe parameters provided by experimentalists(electron density 3e15-3e16, effective mass 0.04me)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parametric overview of the system}
%------------------%
	\subsection{Important metrics}
	We study the influence of the different parameters on the physics of the system by considering a handful of metrics. We list them below, along with how they are computed and what their physical significance is.
		\begin{itemize}
			\item \Gls{Ethouless}
				\begin{align}\label{eq:thouless}
				E_\text{Th} = TN\delta
				, && \delta = \frac{\hbar^2 \pi^2}
				{2 m_e \left( 2 L_m \right)^2}
				\end{align}
			Where $T$ is the transparancy of the junction, and N the number of bands.
			\item Topological invariant: Pfaffian sign
				\subitem The system is extended to infinity and the Pfaffian allows us compute the parity of number of states with positive energy of the system, disregarding the holes. If the resulting topological invariant is -1, we can conclude that if the system were to be made finite, it could potentially support majorana bound states.

@@

			\item Junction transparency
				\subitem The transparency is using kwant. It gives an indication of 
		\end{itemize}
%------------------%
\newpage
	\subsection{Varying magnetic field strength and superconducting phase}
		In this section, we vary the Zeeman field strength and superconducting phase, calculating the topological invariant. 
		From the Pientka paper, we would expect diamond like structures to appear along the magnetic field axis, spaced apart with a distance equal to the Thouless energy. We indeed find this to be the case(figure \ref{fig:lmZPpfaf}). By varying the width of the middle strip we adjust the Thouless energy, and we see clearly find the diamonds shaped apart by the Thouless energy.

		Beyond a certain Zeeman field, we see(although not shown in the figure) that the diamond pattern ceases and turns into stripes independent of phase. At this point, the magnetic field is so strong that bands cross, and our model becomes unphysical. Applying a magnetic field in the superconducting leads as well, lowers the field where this happens.

@@

		In figure \ref{fig:muZnosc}, we plot the system without magnetic field in the leads. With respect to the system with zeeman in the leads, it almost seems like the plot has undergone rescaling. The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes(not shown). We also see that although we can clearly see the gap closing bands(topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.

>>>>

	\begin{align}
		H &= H_0(\tau_z \otimes \sigma_0) + 
		H_\text{Z} (\tau_0 \otimes \sigma_z) +
		(\tau_z \otimes H_\text{SO}) +
	 H_\text{SC}(\tau_y \otimes \sigma_0) \\
		H_0 &= \frac{\hbar^2}{2\meff}\left(\kx^2 + \ky^2\right) - \mu \\
		H_\text{Z} &= g \mu_B B  \left(\Theta(-x) - \Theta(L_m-x)\right)  \\
		H_\text{SO} &= \alpha \left( \ky \sigma_x - \kx \sigma_y \right)\\
		H_\text{SC} &= \Delta \exp \left(i \theta \Theta(x-L_m) \right)
	\end{align}
	Where: 
	\begin{equation}
	\Theta(x) = 
	\begin{cases}
	1,& x>0\\
	0,& \text{otherwise}
	\end{cases}
	\end{equation}
	\subsection{Assumptions and limitations of model}
%		[TODO: LIST ASSUMPTIONS AND LIMITATIONS: SPIN ORBIT DRESSELHAUS, SC MODEL, ETC.]
	\subsection{System parameters}
	\begin{table}
		\begin{tabular}{|c|c|c|c|}
			\hline 
			Variable & Description & Typical value & Default value \\ 
			\hline 
			$g_\text{factor}$ & Magnetic g-factor of material & ~10 & 10 \\ 
			\hline 
			$\mu$ & Chemical potential &  10 - 30 meV & 1 meV\\ 
			\hline 
			$\alpha$ & Spin orbit coupling strength &  30 meV nm & 30 meV nm \\ 
			\hline 
			$\Delta$ & Superconducting gap & 0.2 - 0.3 meV & 0.18 meV\\ 
			\hline 
			$B$ & In-plane magnetic field strength along stripe direction(y) & 0 - 1 T & 0.2 T \\ 
			\hline 
			$\phi$ & Relative phase between superconductors &  0 - 2$\pi$ & $\pi$\\ 
			\hline 
			$\text{L}_\text{l}$ & Width of left superconductor & $\infty$ & 500 nm \\
			\hline 
			$\text{L}_\text{r}$ & Width of right superconductor & $\infty$ & 500 nm \\
			\hline
			$\text{L}_\text{m}$ & Width of middle "normal" strip & 100 - 1000 nm & 250 nm \\
			\hline
			$\text{L}_\text{y}$ & Length of system & \textgreater1000 nm & 4000 nm\\
			\hline
			$T$ & Temperature of system & 0.25 - 1.2K & 0 K\\
			\hline
		\end{tabular} 
	\caption{Description of system parameters, along with typical valuses, as well as a default value which is the used value when no other value has been specified.}
	\label{tbl:system_pars}
	\end{table}
	Describe parameters provided by experimentalists(electron density 3e15-3e16, effective mass 0.04me)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parametric overview of the system}
%------------------%
	\subsection{Important metrics}
	We study the influence of the different parameters on the physics of the system by considering a handful of metrics. We list them below, along with how they are computed and what their physical significance is.
		\begin{itemize}
			\item \Gls{Ethouless}
				\begin{align}\label{eq:thouless}
				E_\text{Th} = TN\delta
				, && \delta = \frac{\hbar^2 \pi^2}
				{2 m_e \left( 2 L_m \right)^2}
				\end{align}
			Where $T$ is the transparancy of the junction and $N$ the number of bands.
			\item Topological invariant: the sign of the Pfaffian
				\subitem The system is extended to infinity and the Pfaffian allows us compute the parity of number of states with positive energy of the system, disregarding the holes. If the resulting topological invariant is -1, we can conclude that if the system were to be made finite, it could potentially support majorana bound states.

@@

			\item Junction transparency
				\subitem The transparency is using kwant. It gives an indication of 
		\end{itemize}
%------------------%
\newpage
	\subsection{Varying magnetic field strength and superconducting phase}
		In this section, we vary the Zeeman field strength and superconducting phase, calculating the topological invariant.
		From the Pientka paper, we would expect diamond like structures to appear along the magnetic field axis, spaced apart with a distance equal to the Thouless energy.
		We indeed find this to be the case (figure \ref{fig:lmZPpfaf}).
		By varying the width of the middle strip we adjust the Thouless energy, and we see clearly find the diamonds shaped apart by the Thouless energy.

		Beyond a certain Zeeman field, we see (although not shown in the figure) that the diamond pattern ceases and turns into stripes independent of phase.
		At this point, the magnetic field is so strong that bands cross, and our model becomes unphysical.
		Applying a magnetic field in the superconducting leads as well, lowers the field where this happens.

@@

		In figure \ref{fig:muZnosc}, we plot the system without magnetic field in the leads.
		With respect to the system with zeeman in the leads, it almost seems like the plot has undergone rescaling.
		The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes(not shown).
		We also see that although we can clearly see the gap closing bands (topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.
